Paper_Figure

### 2025-04-21 README.Rmd
add_citation_adjust_figure
250421

<!-- README.md is generated from README.Rmd. Please edit that file -->

@@

```{r pressure, echo=FALSE, out.width="50%", out.height="auto"}
knitr::include_graphics("./man/figures/LMD_workflow.png")
```

@@

>>>>

@@

```{r pressure, echo=FALSE, out.width="100%", out.height="auto"}
knitr::include_graphics("./man/figures/LMD_workflow.png")
```

@@

### Docker installation

Alternatively, we provide an option of installing LocalizedMarkerDetector with the accompanied lmd docker environment. The pre-built docker image can be downloaded using

``` bash
docker pull ruiqi0130/lmd:lastest
```

and to run the docker container:

``` bash
docker run -it --rm -e USER=john -e USERID=$(id -u) --name container_name -p 8029:8787  -v /data/:/data/   docker.io/jyc34/bipca-experiment:lastest
```

Here, change `/data:/data to `<your_local_data_directory>:/data`. A rstudio will be on port 8029. If you would like to link a local bipca installation (for package development, for instance), you can write -v <your_local_bipca_directory:/bipca.
